Fine-scale Data Reveals Neighborhood Inequalities In Effects of Heat on Expressed Mood

### 2021-08-19 doc/temp-sentiment.tex
pnas submission

\author{}
% \author[1,*]{Matthew Cooper}
% \author[2]{Jeremiah Osborne-Gowey}
% \author[3]{Zheng Liu}
% \author[4]{Portia Adade Williams}
% \author[5]{Jie Liu}
% \author[6]{Aaron Schwartz}
% \author[7]{Patrick Baylis} 
% 
% \affil[1]{T.H. Chan School of Public Health, Harvard University, U.S.A.}
% \affil[2]{Environmental Studies Program, University of Colorado Boulder, U.S.A.}
% \affil[3]{Department of Geographical Sciences, University of Maryland College Park, U.S.A.}
% \affil[4]{CSIR-Science and Technology Policy Research Institute, Ghana}
% \affil[5]{School of Business, East China University of Science and Technology, China} 
% \affil[6]{Department of Ecology \& Evolutionary Biology, University of Colorado Boulder, U.S.A.}
% \affil[7]{Vancouver School of Economics, University of British Columbia, Canada}
% \affil[*]{Corresponding Author: mcooper@hsph.harvard.edu}

@@

\section*{Acknowledgements}
%Official SESYNC wording
This work was supported by the National Socio-Environmental Synthesis Center (SESYNC) under funding received from the National Science Foundation DBI-1639145. Additionally, computational resources for this project were provided for the Microsoft Azure cloud through Microsoft's AI for Earth program.

This data came from Twitter via the University of Vermont’s (UVM) agreement with Twitter to access its streaming API - colloquially referred to as the Decahose. The UVM special agreement with Twitter allows for access to this data for research and analysis purposes and this work complies with all the terms of service for Twitter and UVM.

@@

\noindent This paper was the result of a SESYNC graduate pursuits project co-lead by M.C. and J.O.-G.

>>>>

\author{}
\author[1,*]{Matthew Cooper}
\author[2]{Jeremiah Osborne-Gowey}
\author[3]{Zheng Liu}
\author[4]{Portia Adade Williams}
\author[5]{Jie Liu}
\author[6]{Aaron Schwartz}
\author[7]{Patrick Baylis}

\affil[1]{T.H. Chan School of Public Health, Harvard University, U.S.A.}
\affil[2]{Environmental Studies Program, University of Colorado Boulder, U.S.A.}
\affil[3]{Department of Geographical Sciences, University of Maryland College Park, U.S.A.}
\affil[4]{CSIR-Science and Technology Policy Research Institute, Ghana}
\affil[5]{School of Business, East China University of Science and Technology, China} 
\affil[6]{Department of Ecology \& Evolutionary Biology, University of Colorado Boulder, U.S.A.}
\affil[7]{Vancouver School of Economics, University of British Columbia, Canada}
\affil[*]{Corresponding Author: mcooper@hsph.harvard.edu}

@@

% \section*{Acknowledgements}
%Official SESYNC wording
% This work was supported by the National Socio-Environmental Synthesis Center (SESYNC) under funding received from the National Science Foundation DBI-1639145. Additionally, computational resources for this project were provided for the Microsoft Azure cloud through Microsoft's AI for Earth program.

% This data came from Twitter via the University of Vermont’s (UVM) agreement with Twitter to access its streaming API - colloquially referred to as the Decahose. The UVM special agreement with Twitter allows for access to this data for research and analysis purposes and this work complies with all the terms of service for Twitter and UVM.

@@

% \noindent This paper was the result of a SESYNC graduate pursuits project co-lead by M.C. and J.O.-G.
